---
title: Creating code chunks
author: Matt Malishev
date: '2019-12-09'
slug: Creating-code-chunks
categories:
  - south america
  - mde
tags:
  - south america
  - mde
output:
blogdown:
  html_page:
    code_folding: show
    df_print: paged
    highlight: tango
    toc: true
---

<!-- this enables math encoding in the knitted documents  -->
<script type="text/x-mathjax-config">
  MathJax.Hub.Config({ TeX: { equationNumbers: {autoNumber: "all"} } });
</script>

```{r, set-options, echo = F, cache = T,message=F}
knitr::opts_chunk$set(
 eval = T, # run all code
 echo = T, # show code chunks in output 
 tidy=TRUE, # make output as tidy
 message = F,  # mask all messages
 warning = F, # mask all warnings 
 out.width="100%",
 size="small" # set code chunk size, 
)

### run this once  
# tinytex::install_tinytex()
# require(tinytex)
# install.packages("pacman")
# require(pacman)

suppressWarnings(pacman::p_load(dplyr,ggplot2,plotly,DT,htmlwidgets,viridis,reticulate))
# update.packages("htmlwidgets")

```


# Testing code chunk outputs  

The below code should be highlighted. 

```{r}
require(plotly)
gdf <- data.frame("A" = sample(500),
                  "B" = sample(500))
require(ggplot2)
p <- ggplot(gdf,aes(A,B))+geom_point(color="pink",size=3,show.legend = F) + geom_line(color="black",show.legend = F) + labs(title="Random plot data") + theme_minimal()
ggplotly(p)

```


```{r}

devtools::install_github("jcheng5/d3scatter")
require(pacman)
p_load(d3scatter,crosstalk,leaflet,tibble,httpuv)

sd <- SharedData$new(quakes[sample(nrow(quakes), 100),])

bscols(widths = c(12, 6, 6),
       filter_slider("stations", "Stations", sd, ~stations),
       leaflet(sd, width = "100%", height = 400) %>% 
         addTiles() %>% 
         addCircleMarkers(lng=sd$data()[,"long"],
                    lat=sd$data()[,"lat"],
                    stroke = F,
                    fill = T,
                    color = "red",
                    fillOpacity = 0.5,
                    radius = ~mag + 2,
                    label = ~paste0("Depth: ",as.character(depth))
                    ),
       d3scatter(sd, width = "100%", height = 400, ~mag, ~depth, color = ~stations)
)

```


\newpage



## Use buttons or tabs for sub-chapters {.tabset .tabset-fade .tabset-pills}   

### Chapter 1  

.
.
.
.
.

*Then you can add whatever you want here* like you would normally write in the `Rmd` file.

.
.
.
.
.


### Chapter 2 (with new code)  
Here's an Easter egg for you ...  

```{r,echo=F,message=F}
suppressWarnings(pacman::p_load(plotly,ggplot2))
set.seed(12) # set a number seed for reproducible number results
nn <- 100

random_data <- data.frame("X" = rnorm(nn),
           "Y" = sample(nn/2,nn,replace=T),
           "NN" = nn)

p <- ggplot() +
  geom_point(data=random_data,aes(X,Y,
                 colour=rainbow(nn),
                 size=sample(Y)/5),
                 alpha=abs(rnorm(nn))) +
  labs(x = "Random normally distributed data",
       y = "Sampled integers") +
  theme_minimal() +
  theme(legend.position='none')
ggplotly(p,tooltip=c("X","Y"))

```

### More tables  
Here's a new way of creating tables using the `DT` package  

```{r,cache=T,warning=F, echo=F}
suppressWarnings(pacman::p_load(DT,htmlwidgets))
caption <- "Table 1. The 'mtcars' dataset presented in a datatable. Try editing the columns and cells."
datatable(mtcars,
          rownames = T,
          filter="top",
          options = list(pageLength = 5, scrollX=T),
          class = "cell-border stripe",
          editable = "cell",
          caption = caption
          )
```


<!-- *** -->





